### 2018-11-28 chapters/3-results.tex
readability

ROC analysis was performed for each texture feature. The resulting best features
are shown in Table~\ref{tab:texture_imagetype}. The best one was MBB-GLCM
homogeneity in T₂w with AUC of 0.84.

@@

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Both L1 and L2 regularization methods were
utilized separately. Table~\ref{tab:auc_imagetype} contains the results for
models within each image type using all or top 1\% of the features. The results
are ROC AUC values with confidence intervals included.

>>>>

ROC analysis was performed for each texture feature. The resulting best features
are shown in Table~\ref{tab:texture_imagetype}. The best one was MBB-GLCM
homogeneity in T₂w with AUC=0.84.

@@

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Both L1 and L2 regularization methods were
utilized separately. Table~\ref{tab:auc_imagetype} contains the results for
models within each image type using all of the features and top 1\% of them. The
results are presented as ROC AUC values along with 95\% confidence intervals.
